Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Re-writing comparison

MUSES is mainly a free, open-source, platform independent solution, so these set of features make it a very good option in a first comparison against most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2). In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also  covers laptops and company PCs too, thus, it is not only for BYOD. Moreover the companies which desire work with those systems need a specific operating system and server (such as Windows Server, for instance), being even more strict in some cases, as in Samsung Knox, in which companies must work with a specific (though they can choose from a list) MDM service of being able of deploy Knox in their environments, or in the use of the Blackphone. MUSES is a good solution in these cases, since it is a multiplatform system.

Another comparison concerns that the existing products are mostly policy-based, but MUSES makes its decisions not only considering policies, but also based on the terminals/users context (location, connected networks and so on), to really understand the real danger of a specific action, i.e. it adds a Risk Analysis Process (performed in the RT2AE).

@@

Moreover, another clear advantage over the rest is that MUSES can work in two connection modes, depending on the client being able to connect with the server or not, which favours a real-time decision making process.

Though these are clearly advantages of MUSES over the aforementioned products, they also establish a progress beyond the state of the art with respect to the existing solutions. Other issues that MUSES aims to progress on are related to risk and trust data analysis, human-computer interaction (or HCI), device monitoring, and legal compliance.

>>>>

MUSES is mainly a free, open-source, platform independent solution, and that makes it a very good option in a first comparison against most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2). In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also  covers laptops and company PCs too, thus, it is not only for BYOD. Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server (such as Windows Server, for instance), being even more restrictive in some cases. This is specially remarkable in the case of the Blackphone, forcing the companies and the employees to purchase a specific device. MUSES is a good solution towards these cases, since it is a multiplatform system in both the client and the server.

Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals/users context (connection properties, or trust value of the device, for instance), to really understand the real risk thas comes with a specific action.

@@

Moreover, another clear advantage over the rest is that MUSES can work in both online and offline modes, depending on the client being able to connect with the server or not, which favours a real-time decision making process.

These are not only advantages of MUSES over the existing products, but also a progress beyond the state of the art in some fields like risk and trust analyris, event correlation, and human-computer interaction (HCI).
